The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-18 manuscript/manuscript.Rnw
mention per-species go analyses

>>>>

% \subsubsection{Per-species Gene Set and Pathway Enrichment}

We performed \ac{gsea} on both the top 1\% of transcripts
(Supplemental \cref{tab:go_terms_enriched_top_one_ateles_fusciceps,
  tab:go_terms_enriched_top_one_homo_sapiens,
  tab:go_terms_enriched_top_one_pan_paniscus,
  tab:go_terms_enriched_top_one_mus_musculus,
  tab:go_terms_enriched_top_one_spalax_galili,
  tab:go_terms_enriched_top_one_spalax_carmeli,
  tab:go_terms_enriched_top_one_bos_taurus,
  tab:go_terms_enriched_top_one_ovis_aries,
  tab:go_terms_enriched_top_one_sus_scrofa,
  tab:go_terms_enriched_top_one_equus_caballus,
  tab:go_terms_enriched_top_one_canis_familiaris,
  tab:go_terms_enriched_top_one_loxodonta_africana,
  tab:go_terms_enriched_top_one_dasypus_novemcinctus,
  tab:go_terms_enriched_top_one_monodelphis_domestica}) and the top
100 transcripts (Supplemental
\cref{tab:go_terms_enriched_ateles_fusciceps,
  tab:go_terms_enriched_homo_sapiens,
  tab:go_terms_enriched_pan_paniscus,
  tab:go_terms_enriched_mus_musculus,
  tab:go_terms_enriched_spalax_galili,
  tab:go_terms_enriched_spalax_carmeli,
  tab:go_terms_enriched_bos_taurus, tab:go_terms_enriched_ovis_aries,
  tab:go_terms_enriched_sus_scrofa,
  tab:go_terms_enriched_equus_caballus,
  tab:go_terms_enriched_canis_familiaris,
  tab:go_terms_enriched_loxodonta_africana,
  tab:go_terms_enriched_dasypus_novemcinctus,
  tab:go_terms_enriched_monodelphis_domestica}); common processes
include protein transport and viral transcription/expression
(Supplemental \cref{tab:go_terms_all_species}).
